Simulation of Congenital Heart Defect Corrective Surgeries Using Thin Shell Elements

### 2012-03-01 Doc/Miccai/introduction.tex
fixing my name and adding comments to intro
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@365 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

To be able to predict the result of complex surgical procedures, a physically correct simulation is mandatory. \cite{Li2009} present a {\itshape predictive} surgical simulation system for bidirectional Glenn shunts and basically similar surgeries. The authors use a hybrid model to simulate deformations of blood vessels by binding a surface mesh to a reference Cosserat rod REF elastically. While the mesh models surface details of blood vessels, the Cosserat rod models global deformations, i.e. stretching, bending, twisting and shearing. \stefan{We can delete this: (}Joining of blood vessels end-to-end or end-to-side is realized by attaching contracting springs. This approach adds surplus energy to the physical system and special care has to be taken during the simulation to compensate for that.\stefan{)} The software performs low-level surgical procedures automatically with only a minimum of interaction required which allows the surgeon to focus on the actual overall surgical procedure. Given the input of the surgeon, a complete simulation takes only seconds to produce a predictive result for further examination and evaluation of possibly undesired collisions or deformations of blood vessels. 
Although the results are promising, the method is limited to operations on uniform tubular structures that do not arbitrarily change the surface. Surgical procedures heavily changing surface details of blood vessels, i.e. patches for correction of complicated coarctations and stenosis, are not possible with this hybrid model since the physical behavior of blood vessels is simulated by the Cosserat rod and its {\itshape binding} to the surface mesh.
\christian{I think this paragraph is much too long and I think that our paper should not be presented in opposition to \cite{Li2009} but in the continuity of this work !!  I put a correction of this in a commit 2 days ago, could we try to merge ?} \stefan{I already took your comments into account and tried to present our approach as a consequent continuity of this work. The paragraph was shortened by some sentences also (see the comments in the bottom of the Tex-File. I'm not sure if we should further shorten this paragraph \emph{especially} when we present our work as continuity. Because that paragraph is also an introduction for our work then, isn't it? In the end the paragraph says what can be improved to justify our improved approach. Maybe when we just delete the "alternative" in the next paragpraph?}

>>>>

To be able to predict the result of complex surgical procedures, a physically correct simulation is mandatory. \cite{Li2009} presents a {\itshape predictive} surgical simulation system for bidirectional Glenn shunts and basically similar surgeries. The authors use a hybrid model to simulate deformations of blood vessels by binding a surface mesh to a reference Cosserat rod REF elastically. While the mesh models surface details of blood vessels, the Cosserat rod models global deformations, i.e. stretching, bending, twisting and shearing.
\stefan{We can delete this: (}Joining of blood vessels end-to-end or end-to-side is realized by attaching contracting springs. This approach adds surplus energy to the physical system and special care has to be taken during the simulation to compensate for that.\stefan{)}
\tomas{We can remove this also: (} The software performs low-level surgical procedures automatically with only a minimum of interaction required which allows the surgeon to focus on the actual overall surgical procedure. Given the input of the surgeon, a complete simulation takes only seconds to produce a predictive result for further examination and evaluation of possibly undesired collisions or deformations of blood vessels.\tomas{) Or replace with shorter: The surgeon's input is limited to point-and-click and the software performs low-level surgical procedures automatically.}
Although the results are promising, the method is limited to operations on uniform tubular structures that do not arbitrarily change the surface. Surgical procedures heavily changing surface details of blood vessels, i.e. patches for correction of complicated coarctations and stenosis, are not possible with this hybrid model since the physical behavior of blood vessels is simulated by the Cosserat rod and its {\itshape binding} to the surface mesh.
\christian{I think this paragraph is much too long and I think that our paper should not be presented in opposition to \cite{Li2009} but in the continuity of this work !!  I put a correction of this in a commit 2 days ago, could we try to merge ?} \stefan{I already took your comments into account and tried to present our approach as a consequent continuity of this work. The paragraph was shortened by some sentences also (see the comments in the bottom of the Tex-File. I'm not sure if we should further shorten this paragraph \emph{especially} when we present our work as continuity. Because that paragraph is also an introduction for our work then, isn't it? In the end the paragraph says what can be improved to justify our improved approach. Maybe when we just delete the "alternative" in the next paragpraph?}
